---
title: "Mice1"
author: "Jonah Mahen, Austin Lopez"
date: "3/27/2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

### Description

We will be writing code for data from BioSeb Dynamic Weight Bearing Pain Analysis. The data is for pain differences in different destabilization surgeries in mice. We will organize the data into groups and analyze the data using a t test and put the data into graphs.  

### Summary of Roles

Austin:
Completed: Exporting of data files, separation into subject, group, and date of acquisition. 
Now, the data points will be combined and sorted using R.

Jonah:
Using R script, data points will be separated and combined into graphs showing data analysis. 

### Resources 

We obtained our data from the BioSeb Dynamic Weight Bearing Pain analysis. This data came from the Oklahoma Medical Research Foundation's study on osteoarthritis in mice. Austin was given access to this data at OMRF. The code for the graphs and the t test comes from the Rintro.rmd file provided in GNSC-3301. 

### Progress thus far

Up to this point, we have obtained the data that will be used from OMRF. Austin has exported the data and grouped the data into subject, date, and group. Austin still needs to sort the data points using R and then I will be creating graphs and analyzing the data using a t-test.

# Load your dataset
```{r} 
my_data <- read.csv("ComputingMiceMain.csv")
Groups <- read.table(header=TRUE, row.names=2, text="
Groups Samples
1-FMRLb6DMM 87780
1-FMRLb6DMM 107467
2-Mb6VEHDMMPA 97478
2-Mb6VEHDMMPA 97497
2-Mb6VEHDMMPA 87786
3-Mb6CPA 107455
3-Mb6CPA 107463
4-b6MRLDMMPA 97479
4-b6MRLDMMPA 107442
5-MRLVEHDMM 87782
5-MRLVEHDMM 97502
5-MRLVEHDMM 97494
6-MRLCPA 117067
6-MRLCPA 117068
")
my_data$Group <- Groups[as.character(my_data$Sample_group), "Groups"]
```

# Histogram
```{r}

hist(my_data$Posture.Duration..s., breaks=50, col="skyblue", main="Distribution of Posture Duration", xlab="Posture Duration (sec)")

## hist(subset(my_data, subset=(Group=="6-MRLCPA"))$Rear.Left.Rear.Right.Area.Ratio,breaks=20,col="skyblue", main="Distribution of Posture Duration", xlab="Posture Duration (sec)")

for (graph in levels(as.factor(my_data$Group))) {hist(subset(my_data, subset=(Group==graph))$Rear.Left.Rear.Right.Area.Ratio,breaks=20,col="skyblue", main=graph, xlab="Posture Duration (sec)")}

```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
Mice <- aov(Rear.Left.Rear.Right.Area.Ratio~Group, data= my_data)
summary(Mice)
```

```{r}
BrokenMouse <- TukeyHSD(Mice)
BrokenMouse
plot(BrokenMouse)
```