---
title: "Mice1"
author: "Jonah Mahen, Austin Lopez"
date: "3/27/2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

### Description

We will be writing code for data from BioSeb Dynamic Weight Bearing Pain Analysis. The data is for pain differences in different destabilization surgeries in mice. We will organize the data into groups and analyze the data using a t test and put the data into graphs.  

### Summary of Roles

Austin:
Completed: Exporting of data files, separation into subject, group, and date of acquisition. 
Now, the data points will be combined and sorted using R.

Jonah:
Using R script, data points will be separated and combined into graphs showing data analysis. 

### Resources 

We obtained our data from the BioSeb Dynamic Weight Bearing Pain analysis. This data came from the Oklahoma Medical Research Foundation's study on osteoarthritis in mice. Austin was given access to this data at OMRF. The code for the graphs and the t test comes from the Rintro.rmd file provided in GNSC-3301. 

### Progress thus far

Up to this point, we have obtained the data that will be used from OMRF. Austin has exported the data and grouped the data into subject, date, and group. Austin still needs to sort the data points using R and then I will be creating graphs and analyzing the data using a t-test.

# Load your dataset
```{r} 
my_data <- read.csv("ComputingMiceMain.csv")
```

# Histogram
```{r}

hist(my_data$Posture.Duration..s., breaks=50, col="skyblue", main="Distribution of Posture Duration", xlab="Posture Duration (sec)")

```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
